---
title: "Final Paper"
author: "STOR 520 Group 2"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidytext)
library(lubridate)
library(DT)
library(patchwork)
anime1=read_csv('https://opal.ils.unc.edu/~theozh/Anime-2.csv')
 
```

## Introduction

## Data

## Results
#### Part I

In Japanese, "shoujo" literally means girls and "shounen" means boys. Shoujo anime are typically geared towards young girls and women, while "shounen" anime are geared towards young boys and men, typically between the ages of 12 and 18. We focused on the **Demographics** variable from the complete anime dataset that contains more than 20,000 entries. This filtered dataset serves as a repository for us to gain meaningful insights into the world of both shoujo and shounen anime, as we intend to explore young women’s and men’s preferences and interests in anime.

After applying the tidytext library to perform an innerjoin() with the Bing lexicon, which categorizes words into two groups: positive +1 and negative -1, we aggregated the scores to produce an overall sentiment score year-on-year for the text from the **Synopsis** variable. Our aim is to analyze the trend in sentiment over time.

It seems that from 1966 to 2022, the sentiment scores for both shoujo and shounen anime appear to remain relatively stable, which suggests that both types of anime tend to maintain a relatively consistent emotional tone over time. However, the graph also shows that shoujo anime has a slightly higher positive sentiment score than shounen anime. This indicates that shoujo anime may have more elements of happiness, joy, and love, while shounen anime may have more elements of sadness, anger, and violence. These differences reflect the different preferences and interests of their target demographics.

It’s also interesting to explore the extreme spikes in negative sentiment scores. This suggests that something specific may have influenced the emotional tone of shoujo anime in those particular years. Case in point is the anime “Pretty Guardians Sailor Moon Eternal The Movie Part 2”, released in 2021. The portrayal of a post-solar eclipse Earth being shrouded in a dark force suggests a potentially dire and challenging situation for the characters, hence a strong negative sentiment.


```{r, echo=F, warning=F, message=FALSE}
shoujo_data=anime1 %>% 
  filter(Demographics == "Shoujo") %>% 
  select(-3,-4, -9, -c(11:16)) %>% 
  rename(Minutes=Duration_Minutes) 

shoujo_data$Start_Aired = as.Date(shoujo_data$Start_Aired, format = "%d-%b-%y")
future_dates = !is.na(shoujo_data$Start_Aired) & shoujo_data$Start_Aired > Sys.Date()
shoujo_data$Start_Aired[future_dates] = shoujo_data$Start_Aired[future_dates] - years(100)
shoujo_data$Year <- format(shoujo_data$Start_Aired, "%Y")

 
shounen_data=anime1 %>% 
  filter(Demographics == "Shounen") %>% 
  select(-3,-4, -9, -c(11:16)) %>% 
  rename(Minutes=Duration_Minutes) 

shounen_data$Start_Aired = as.Date(shounen_data$Start_Aired, format = "%d-%b-%y")
future_dates = !is.na(shounen_data$Start_Aired) & shounen_data$Start_Aired > Sys.Date()
shounen_data$Start_Aired[future_dates] = shounen_data$Start_Aired[future_dates] - years(100)
shounen_data$Year <- format(shounen_data$Start_Aired, "%Y")
```


```{r, echo=F, warning=F, message=FALSE}

bing_lexicon = get_sentiments("bing")
process_sentiment_data <- function(dataset) {
  dataset_tokens <- dataset %>%
    mutate(Synopsis = tolower(Synopsis)) %>%
    unnest_tokens(word, Synopsis)

  dataset_sentiment_by_anime <- dataset_tokens %>%
    inner_join(bing_lexicon) %>%
    count(Start_Aired, sentiment) %>%
    spread(sentiment, n, fill = 0) %>%
    mutate(Sentiment = positive - negative)

  return(dataset_sentiment_by_anime)
}

# Apply the function to shoujo_data and shonen_data
shoujo_sentiment_by_anime <- process_sentiment_data(shoujo_data)
shounen_sentiment_by_anime <- process_sentiment_data(shounen_data)
```


```{r, echo=F, warning=F, message=FALSE}
shoujo_sentiment_by_anime$Start_Aired[is.na(shoujo_sentiment_by_anime$Start_Aired)] = median(shoujo_sentiment_by_anime$Start_Aired, na.rm = TRUE)
shounen_sentiment_by_anime$Start_Aired[is.na(shounen_sentiment_by_anime$Start_Aired)] = median(shounen_sentiment_by_anime$Start_Aired, na.rm = TRUE)

# Plotting both shoujo and shounen sentiment on the same plot
ggplot() +
  geom_point(data = shoujo_sentiment_by_anime, aes(Start_Aired, Sentiment, group = 1, color = "Shoujo")) +
  geom_point(data = shounen_sentiment_by_anime, aes(Start_Aired, Sentiment, group = 1, color = "Shounen"), alpha=0.4) +
  geom_smooth(data = shoujo_sentiment_by_anime, method='lm', se=FALSE, aes(Start_Aired, Sentiment, group = 1), color = "red") +
  geom_smooth(data = shounen_sentiment_by_anime, method='lm', se=FALSE, aes(Start_Aired, Sentiment, group = 1), color = "darkblue") +
  labs(title = "Sentiment Trends Over Years",
       x = NULL,
       y = "Sentiment Score",
       color = "Anime Demographics") +
  theme_bw() +
  scale_x_date(breaks = scales::breaks_pretty(n = 12))
```

From the bar plots of the top 10 positive and negative terms for both anime, with error bars indicating the 95% confidence intervals, the highest frequency of the term "love" suggests a strong emphasis on romantic themes within the shoujo anime. “Love” significantly outranks the other tersm, more than twice as frequent as the second term “magical”. This corresponds with our preconceived notion that young women often have a preference for romance in their anime choices. It indicates that romance remains a potent and popular theme for shoujo anime audiences. The rest of the top terms suggest themes of magic, admiration, healing, excellence, and popularity.

In shounen anime, the top positive terms suggest themes of personal growth, power, victory, protection, and mastery. These themes are common in shounen anime, which often feature young male protagonists who strive to become stronger, protect others, and overcome challenges. The relatively even distribution of these terms indicates a balance of these themes in shounen anime.

The term “mysterious” appearing as the top negative term in both shoujo and shounen anime might be due to the nature of storytelling in these anime. The term “mysterious” might be categorized as negative because it often implies uncertainty, confusion, or potential danger. But in the context of anime, “mysterious” elements can make the story more engaging and exciting for the viewers. Its frequent appearance could be read as a sign of the richness in plot and character development.


```{r, echo=F, warning=F, message=F, fig.width=10, fig.height=4}
# Function to process data and calculate sentiments
process_data <- function(data, lexicon) {
  tokens <- data %>%
    mutate(Synopsis = tolower(Synopsis)) %>%
    unnest_tokens(word, Synopsis)

  sentiments <- tokens %>%
    inner_join(lexicon) 
  
  return(sentiments)
}

# Function to create plots
plot_sentiments <- function(sentiments, title) {
  positive_terms <- sentiments %>%
    filter(sentiment == "positive") %>%
    count(word, sort = TRUE) %>%
    top_n(10)

  negative_terms <- sentiments %>%
    filter(sentiment == "negative") %>%
    count(word, sort = TRUE) %>%
    filter(word != "unknown") %>% 
    top_n(10)

  combined_terms <- bind_rows(
    mutate(positive_terms, sentiment = "positive"),
    mutate(negative_terms, sentiment = "negative")
  )

  combined_terms <- combined_terms %>%
    group_by(sentiment, word) %>%
    summarise(n = n, lower = n - 1.96*sqrt(n), upper = n + 1.96*sqrt(n))

  ggplot(combined_terms, aes(x = reorder(word, n), y = n, fill = sentiment)) +
    geom_bar(stat = "identity", position = 'dodge') +
    geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2, position = position_dodge(0.9)) +
    labs(title = title,
         x = NULL,
         y = "Frequency") +
    facet_wrap(~ sentiment, scales = "free_y") +
    coord_flip() +
    theme_bw()
}

# Shoujo analysis
shoujo_sentiments <- process_data(shoujo_data, bing_lexicon)
shoujo_plot <- plot_sentiments(shoujo_sentiments, "Top 10 Sentiment-Rich Terms in Shoujo Anime")

# Shounen analysis
shounen_sentiments <- process_data(shounen_data, bing_lexicon)
shounen_plot <- plot_sentiments(shounen_sentiments, "Top 10 Sentiment-Rich Terms in Shounen Anime")

# Print or save plots as needed
print(shoujo_plot)
print(shounen_plot)

```

We then calculated the sentiment score based on their ratings. It's no surprise that "R - 17+ (violence & profanity)" **Rating** has the lowest sentiment score for both shoujo and shounen anime, as this rating normally has more violent, profane, or disturbing content that can affect the viewer’s emotions negatively.

We are suprised to find that the "PG-13 - Teens 13" and "PG-13 - Teens 13" **Rating**, which is supposed to have more enjoyable or relatable content that can elicit more positive emotions, reflects negative sentiment scores within shounen anime. 

```{r, echo=F, warning=F, message=FALSE, fig.width=8, fig.height=2.5}
# Function to aggregate sentiments and calculate statistics
aggregate_sentiments <- function(data) {
  aggregated_data <- data %>%
    group_by(ID) %>%
    summarise(
      English = first(English),
      Type = first(Type),
      Episodes = first(Episodes),
      Start_Aired = first(Start_Aired),
      Year = first(Year),
      Genres = first(Genres),
      Themes = first(Themes),
      Minutes = first(Minutes),
      Rating = first(Rating),
      Score = first(Score),
      Scored_Users = first(Scored_Users),
      Ranked = first(Ranked),
      Popularity = first(Popularity),
      Members = first(Members),
      Favorites = first(Favorites),
      sentiment = sum(ifelse(sentiment == "positive", 1, -1))
    ) 

  rating_groups <- split(aggregated_data, aggregated_data$Rating)

  sentiment_stats <- lapply(rating_groups, function(group) {
    n = nrow(group)
    mean_sentiment = mean(group$sentiment)
    sd_sentiment = sd(group$sentiment)

    ci_lower = mean_sentiment - 1.96 * sd_sentiment / sqrt(n)
    ci_upper = mean_sentiment + 1.96 * sd_sentiment / sqrt(n)

    return(data.frame(Mean_Sentiment = mean_sentiment, 
                      CI_lower = ci_lower,
                      CI_upper = ci_upper))
  })

  sentiment_stats_df <- do.call(rbind, sentiment_stats)
  rownames(sentiment_stats_df) = names(sentiment_stats)

  return(list(aggregated_data = aggregated_data, sentiment_stats_df = sentiment_stats_df))
}

# Shoujo analysis
shoujo_results <- aggregate_sentiments(shoujo_sentiments)

# Shounen analysis
shounen_results <- aggregate_sentiments(shounen_sentiments)

# Access aggregated data and sentiment statistics
shoujo_sentiments_aggregated <- shoujo_results$aggregated_data
shoujo_sentiment_stats <- shoujo_results$sentiment_stats_df %>% 
   filter(row.names(.) != 'None')

shounen_sentiments_aggregated <- shounen_results$aggregated_data
shounen_sentiment_stats <- shounen_results$sentiment_stats_df %>% 
   filter(row.names(.) != 'None')

# Plot for Shoujo
shoujo_rating = ggplot(shoujo_sentiment_stats, aes(x = rownames(shoujo_sentiment_stats), y = Mean_Sentiment, fill = ifelse(Mean_Sentiment > 0, "positive", "negative"))) +
  geom_bar(stat = "identity", width = 0.5) +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper), width = 0.2) +
  labs(x='', y = "Mean Sentiment", title = 'Sentiment by Ratings in Shoujo Anime') +
  coord_flip() +
  scale_fill_manual(values = c("positive" = "cornflowerblue", "negative" = "lightsalmon")) +
  theme_bw()+
  theme(legend.position = "none")

# Plot for Shounen
shounen_rating = ggplot(shounen_sentiment_stats, aes(x = rownames(shounen_sentiment_stats), y = Mean_Sentiment, fill = ifelse(Mean_Sentiment > 0, "positive", "negative"))) +
  geom_bar(stat = "identity", width = 0.5) +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper), width = 0.2) +
  labs(x='', y = "Mean Sentiment", title = 'Sentiment by Ratings in Shounen Anime') +
  coord_flip() +
  scale_fill_manual(values = c("positive" = "cornflowerblue", "negative" = "lightsalmon")) +
  theme_bw()+
  theme(legend.position = "none")


shoujo_rating
shounen_rating
```

We proceeded to draw two heatmaps based on the average popularity score from the **Favorites** variable for different theme and genre combinations. This involves grouping the data by the **Themes** and **Genres** variables. The **Favorites** variable represents the number of users who have marked the anime as their favorite anime.

The most popular combinations of theme and genre for shoujo anime are "Action" and "Delinquent". This combination suggests that viewers of shoujo anime appreciate narratives that involve conflict, action, and characters who are rebellious or non-conforming. This could indicate a desire for stories that break away from traditional norms and expectations, reflecting the complexities and challenges of adolescence. Shoujo anime viewers also love any combination of "Adult Cast" with either "Drama", "Romance", or "Slice of Life". It might due to their vested interest in mature and realistic narratives. They might appreciate stories that deal with adult relationships, emotional conflicts, and everyday life experiences. 

As expected from young male audiences, popular combinations for shounen anime viewers include “Suspense" and "Gore”, and “Adventure" and "Organized Crime”, all of which suggest a preference for narratives that balance emotional depth with thrilling action, survival challenges, and criminal intrigue. However, the most favored combination is “Drama” and “Romantic Subtext”, with over 70,000 viewers adding it to their favorites. This is much higher than any other combination by a wide gap. While it may come as a surprise, it appears that young male viewers do have a strong preference for narratives that delve into emotional depth and subtle romantic elements. This is despite the fact that shounen anime is typically associated with action and adventure themes. Our guess is that overtly romantic themes can sometimes fall into cliche story lines. Romantic subtext allows for a more subtle and nuanced exploration of romantic elements. This can appeal to a broader audience, including those who may not typically seek out explicit romance stories.



```{r, echo=F, warning=F, message=FALSE, fig.width=8, fig.height=3}
anime2 = shoujo_data %>%
  separate_rows(Themes, sep = ", ") %>%
  separate_rows(Genres, sep = ", ")

combinations = expand.grid(unique(anime2$Themes), unique(anime2$Genres))
colnames(combinations) = c("Themes", "Genres")

combinations = combinations %>%
  mutate(Avg_Popularity = sapply(1:nrow(combinations), function(i) {
    theme = combinations$Themes[i]
    genre = combinations$Genres[i]
    avg_popularity = mean(anime2$Favorites[anime2$Themes == theme & anime2$Genres == genre], na.rm = TRUE)
    return(avg_popularity)
  })) 

combinations = combinations %>%
  arrange(desc(Avg_Popularity))


# Assuming you have the 'combinations' data frame

# Filter for the top 20 combinations
top_combinations <- combinations %>%
  top_n(30, Avg_Popularity)

heatmap_plot <- ggplot(top_combinations, aes(x = Themes, y = Genres, fill = Avg_Popularity)) +
  geom_tile(color = "white") +
  geom_text(aes(label = round(Avg_Popularity)), color = "black", size = 3) +  # Round to integer and add text labels inside the tiles
  scale_fill_gradient2(low = "white", mid = "lightpink", high = "red", midpoint = median(top_combinations$Avg_Popularity), guide = "colorbar") +  # Blue-to-red gradient
  labs(title = "Top 30 Popular Themes and Genres Combinations in Shoujo Anime",
       x = "Themes", y = "Genres", fill = "Average Popularity") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 25, hjust = 1))  # Adjust hjust for title position

heatmap_plot



anime3 = shounen_data %>%
  separate_rows(Themes, sep = ", ") %>%
  separate_rows(Genres, sep = ", ")

combinations = expand.grid(unique(anime3$Themes), unique(anime3$Genres))
colnames(combinations) = c("Themes", "Genres")

combinations = combinations %>%
  mutate(Avg_Popularity = sapply(1:nrow(combinations), function(i) {
    theme = combinations$Themes[i]
    genre = combinations$Genres[i]
    avg_popularity = mean(anime3$Favorites[anime3$Themes == theme & anime3$Genres == genre], na.rm = TRUE)
    return(avg_popularity)
  })) 

combinations = combinations %>%
  arrange(desc(Avg_Popularity))


# Assuming you have the 'combinations' data frame

# Filter for the top 20 combinations
top_combinations <- combinations %>%
  top_n(30, Avg_Popularity)

heatmap_plot <- ggplot(top_combinations, aes(x = Themes, y = Genres, fill = Avg_Popularity)) +
  geom_tile(color = "white") +
  geom_text(aes(label = round(Avg_Popularity)), color = "black", size = 3) +  # Round to integer and add text labels inside the tiles
  scale_fill_gradient2(low = "white", mid = "lightblue", high = "blue", midpoint = median(top_combinations$Avg_Popularity), guide = "colorbar") +  # Blue-to-red gradient
  labs(title = "Top 30 Popular Themes and Genres Combinations in Shounen Anime",
       x = "Themes", y = "Genres", fill = "Average Popularity") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 25, hjust = 1))  # Adjust hjust for title position


heatmap_plot


```



From the bar chart below of the top 10 genres and its corresponding sentiment score, Shounen anime have mostly negative scores. It is expected as shounen anime often involves themes of conflict, violence, tragedy, and hardship. These themes can introduce more negative words and emotions into the synopsis text, such as “death”, “fight”, “kill”, “betrayal”, “suffering”. These words can lower the overall sentiment score of the anime, and consequently, the genre.

As we look at the graphs, we discover that shoujo anime are more fascinating to investigate. The prominence of the romance genre further consolidated my preconception that romantic relationships and themes hold a central position in shoujo anime. The popularity of fantasy genre indicates a desire for escapism and immersion in imaginative worlds. 

However, when we have the scope expanded to the top 15 genres, we find something interesting in terms of sentiment within each genre. Although "Boys Love" and Girls Love" anime are both typically created with a female audience in mind, focusing on the romantic relationships between same-sex characters, BL have a negative sentiment, whereas GL tends to be positive overall. 

Upon research, this might be the answer: BL anime often explores themes of unrequited love or complex relationships. This can introduce more elements of heartbreaks and emotional turmoil. BL anime also often includes elements of sexual tension and can delve into more explicit themes. These complexity could potentially result in a lower sentiment score. This finding is also corroborated by the fact that most of the "R - 17+ (violence & profanity)" shoujo anime also belong to the BL genre. In contrast, GL anime place a stronger emphasis on emotional and spiritual connections between female characters, which often evoke a sense of warmth, understanding and fulfillment. 



```{r, echo=F, warning=F, message=FALSE, fig.width=10, fig.height=4}
shoujo_sentiments_aggregated <- shoujo_sentiments_aggregated %>%
  filter(Genres != 'Unknown')

genres_list = unlist(strsplit(shoujo_sentiments_aggregated$Genres, ", "))
genre_frequencies = table(genres_list)
top_10_genres = head(sort(genre_frequencies, decreasing=T), 10)
top_15_genres = head(sort(genre_frequencies, decreasing=T), 15)

genre_sentiment = sapply(names(top_15_genres), function(genre) {
  mean(shoujo_sentiments_aggregated$sentiment[grepl(genre, shoujo_sentiments_aggregated$Genres)])
})

genre_sentiment_df = data.frame(Genre = names(top_15_genres), Mean_Sentiment = genre_sentiment)
genre_data = data.frame(genre = names(top_10_genres), frequency = as.numeric(top_10_genres))

plot1=ggplot(genre_data, aes(x = "", y = frequency, fill = genre)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y") +
  labs(title = "Top 10 Genres in Shoujo Anime") +
  geom_text(aes(label = paste0(genre, '\n', scales::percent(frequency / sum(frequency))), 
                x = 1.3), 
            position = position_stack(vjust = 0.5),
            size = 2) +
  theme_void() +
  theme(legend.position = "right") +
  scale_fill_brewer(palette = "Set3")+
  theme(legend.position = "none")

genre_sentiment_df$se <- sd(genre_sentiment_df$Mean_Sentiment) / sqrt(nrow(genre_sentiment_df))
genre_sentiment_df$ci <- genre_sentiment_df$se * qt(0.975, df=nrow(genre_sentiment_df)-1)

plot2=ggplot(genre_sentiment_df, aes(x = reorder(Genre, -desc(Mean_Sentiment)), y = Mean_Sentiment, fill = factor(ifelse(Mean_Sentiment >= 0, "Positive", "Negative")))) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(aes(ymin = Mean_Sentiment - ci, ymax = Mean_Sentiment + ci), width = 0.2) +
  scale_fill_manual(values = c("lightsalmon", "cornflowerblue"), labels = c("Negative", "Positive")) +
  labs(title = "Mean Sentiment by Genre in Shoujo Anime", x='',
       y = "Mean Sentiment", fill = "Sentiment")+
  coord_flip() +
  theme_bw()+
  theme(legend.position = "none")




shounen_sentiments_aggregated <- shounen_sentiments_aggregated %>%
  filter(Genres != 'Unknown')

genres_list = unlist(strsplit(shounen_sentiments_aggregated$Genres, ", "))
genre_frequencies = table(genres_list)
top_10_genres = head(sort(genre_frequencies, decreasing=T), 10)
top_15_genres = head(sort(genre_frequencies, decreasing=T), 15)


genre_sentiment = sapply(names(top_15_genres), function(genre) {
  mean(shounen_sentiments_aggregated$sentiment[grepl(genre, shounen_sentiments_aggregated$Genres)])
})

genre_sentiment_df = data.frame(Genre = names(top_15_genres), Mean_Sentiment = genre_sentiment)
genre_data = data.frame(genre = names(top_10_genres), frequency = as.numeric(top_10_genres))

plot3=ggplot(genre_data, aes(x = "", y = frequency, fill = genre)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y") +
  labs(title = "Top 10 Genres in Shounen Anime") +
  geom_text(aes(label = paste0(genre, '\n', scales::percent(frequency / sum(frequency))), 
                x = 1.3), 
            position = position_stack(vjust = 0.5),
            size = 2) +
  theme_void() +
  theme(legend.position = "none") +
  scale_fill_brewer(palette = "Set3")

genre_sentiment_df$se <- sd(genre_sentiment_df$Mean_Sentiment) / sqrt(nrow(genre_sentiment_df))
genre_sentiment_df$ci <- genre_sentiment_df$se * qt(0.975, df=nrow(genre_sentiment_df)-1)

plot4=ggplot(genre_sentiment_df, aes(x = reorder(Genre, -desc(Mean_Sentiment)), y = Mean_Sentiment, fill = factor(ifelse(Mean_Sentiment >= 0, "Positive", "Negative")))) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(aes(ymin = Mean_Sentiment - ci, ymax = Mean_Sentiment + ci), width = 0.2) +
  scale_fill_manual(values = c("lightsalmon", "cornflowerblue"), labels = c("Negative", "Positive")) +
  labs(title = "Mean Sentiment by Genre in Shounen Anime", x='',
       y = "Mean Sentiment", fill = "Sentiment")+
  coord_flip() +
  theme_bw()+
  theme(legend.position = "none")

combined_plots1 <- plot1 + plot2
combined_plots1
combined_plots2 <- plot3 + plot4
combined_plots2

```

#### Part II
???????????





## Conclusion

In our journey to unravel the world of anime, we embarked on an exploratory data  analysis of a comprehensive anime dataset. Our journey marches on deconstructing the intricacy of shoujo and shounen anime that target primarily adolencents. Our initial focus was onconducting a sentiment analysis of the **Synopses**, which served as a window into the emotional landscape of shoujo and shounen anime. The results were fascinating, revealing a relatively stable emotional tone across the years. This consistency suggests that both anime have maintained its core emotional appeal over time, resonating with its audience’s expectations and preferences.  However, our curiosity was piqued by occasional spikes in negative sentiment scores in certain years. These anomalies hinted at specific influences or events that might have temporarily  shifted the emotional tone during those periods. Furthermore, our analysis confirmed the  prominence of romance in shoujo anime, as evidenced by the high frequency of the term  “love”. This finding aligns with the genre’s target demographic of young women, for whom  romantic themes often hold significant appeal. 

Building on these initial insights, we decided to delve deeper into the interplay  between themes, genres, and sentiment scores in our follow-up investigation. Our analysis  revealed a striking contrast in sentiment between “Boys Love” (BL) and “Girls Love” (GL) anime,  although both involve same-sex storylines. BL anime exhibited a more negative sentiment  overall, which could be attributed to its exploration of complex and often emotionally  challenging relationships. Themes such as unrequited love add layers of depth and heartache to  these narratives, contributing to their overall negative sentiment. Conversely, GL anime  showcased a more positive sentiment, often highlighting emotional and spiritual bonds  between female characters. These narratives tend to focus on themes of friendship, mutual  support, and love, creating a more uplifting emotional experience for viewers. This nuanced  understanding of how different themes and genres shape viewer emotions underscores the  diverse dynamics within the shoujo anime genre. By leveraging tables and figures to quantify  and visualize these sentiments, we were able to uncover underlying trends and preferences in these anime. These findings not only enrich our understanding of this targeted demographic but also provide valuable insights for creators and viewers alike. 

In this project of sentiment analysis, we used the Bing lexicon, which is a dictionary of words that have been labeled as either positive or negative. We applied the tidytext package in R to join the Bing lexicon with the **Synopsis** text of each shoujo anime, and then calculated the sentiment score by summing up the polarity values of each word. This score represents the overall emotional tone of the text, which can be used to compare and group different anime based on their sentiment. However, this method has some limitations, such as ignoring the context, sarcasm, or intensity of the words. Therefore, the sentiment scores should not be taken as absolute measures of emotion.










